Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint

### 2020-06-18 analysis/VOCC/1-split-biomass-by-maturity.Rmd
change Bocaccio to a global maturity estimate

---
title: "Split `r paste(params$species)` biomass by maturity class"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Bocaccio"
    species: "Threadfin Sculpin"
    #species: "Quillback Rockfish"
    #species: "Yelloweye Rockfish"
    #species: "Shortraker Rockfish"
    # species: "Pacific Ocean Perch"
    region: "All synoptic surveys"
    # region: "Both odd year surveys"
    threshold: 0.05
    split: FALSE
---

>>>>

---
title: "Split `r paste(params$species)` biomass by maturity class"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Bocaccio"
    # species: "Threadfin Sculpin"
    #species: "Quillback Rockfish"
    #species: "Yelloweye Rockfish"
    #species: "Shortraker Rockfish"
    # species: "Pacific Ocean Perch"
    region: "All synoptic surveys"
    # region: "Both odd year surveys"
    threshold: 0.5
    split: TRUE
---

### 2020-06-18 analysis/VOCC/2-biomass-depth-only-model.Rmd
change Bocaccio to a global maturity estimate

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Redbanded Rockfish"
    #species: "Pacific Ocean Perch"
    #species: "Pacific Cod"
    #species: "Petrale Sole"
    #species: "Widow Rockfish"
    species: "Bocaccio"
    region: "All synoptic surveys"
    knots: 500
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    #covs: "-ssid-only" # covariate string used to name model rds 
    covs: "-tv-depth-only"
    #covs: "-trawled-ssid"
    update_model: FALSE
    update_predictions: FALSE
    update_model_check: FALSE
---

@@

>>>>

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    # species: "Redbanded Rockfish"
    #species: "Pacific Ocean Perch"
    #species: "Pacific Cod"
    #species: "Petrale Sole"
    # species: "Widow Rockfish"
    species: "Bocaccio"
    # species: "Sablefish"
    region: "All synoptic surveys"
    knots: 500
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    #covs: "-ssid-only" # covariate string used to name model rds 
    covs: "-tv-depth-only"
    #covs: "-trawled-ssid"
    update_model: FALSE
    update_predictions: FALSE
    update_model_check: FALSE
---

@@

```{r}
fits <- readRDS("climate-fits.rds")
check_fits <- left_join(depth_only_predictions,fits)

try({
  g3 <- ggplot(check_fits, aes(t_resids, residuals, colour = density)) +
    geom_point() + # scale_x_continuous(trans = 'log10') +
    facet_wrap(~year)
  g4 <- ggplot(check_fits, aes(d_resids, residuals, colour = density)) +
    geom_point() + # scale_x_continuous(trans = 'log10') +
    facet_wrap(~year)
})
try({
  g3 <- ggplot(check_fits, aes(t_resids, residuals, colour = adult_density)) +
    geom_point() + # scale_x_continuous(trans = 'log10') +
    facet_wrap(~year)
  g4 <- ggplot(check_fits, aes(d_resids, residuals, colour = adult_density)) +
    geom_point() + # scale_x_continuous(trans = 'log10') +
    facet_wrap(~year)
})
g3
g4
```
